Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-22 tex/MesnardoBarba2019.tex
Move table (NC series) to cost section
Add table with hardware specs

\usepackage{algorithmic}
\usepackage{array}
 \usepackage[nocompress]{cite}
 \usepackage{color}
\usepackage{listings}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{stfloats}
\usepackage{url}

@@

\begin{table*}[!h]
    \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
    \label{tab:nc_series}
    \centering
    \begin{tabular}{cccccccc}
        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
        \hline
        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.574 & 0.40 \\
        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.147 & 0.80 \\
        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
        \hline
    \end{tabular}
\end{table*}

\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}

@@

>>>>

\usepackage{algorithmic}
\usepackage{array}
 \usepackage[nocompress]{cite}
 \usepackage{color}
\usepackage{listings}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{stfloats}
\usepackage{url}
\usepackage{multirow}

@@

\begin{table*}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{Hardware Specifications of Nodes Used on Microsoft Azure and Colonial One. On Both Platforms, MPI Applications Take Advantage of RDMA (Remote Direct Memory Access) Network with FDR InfiniBand.}
    \label{tab:hw_specs}
    \centering
    \begin{tabular}{cccccccc}
        Platform & Node & Intel Xeon CPU & \# threads & NVIDIA GPU & RAM (GiB) & SSD Storage (GiB) \\
        \hline
        \multirow{2}{*}{Azure} & NC24r & Dual 12-Core E5-2690v3 (2.60GHz) & 24 & 4 x K80 & 224 & 1440 \\
        & H16r & Dual 8-Core E5-2667v3 (3.20GHz) & 16 & - & 112 & 2000 \\
        \hline
        \multirow{2}{*}{Colonial One} & Ivygpu & Dual 6-Core E5-2620v2 (2.10GHz) & 12 & 2 x K20 & 120 & 93 \\
        & Short & Dual 8-Core E5-2650v2 (2.60GHz) & 16 & - & 120 & 93 \\
        \hline
    \end{tabular}
\end{table*}

@@

\begin{table*}[!h]
    \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
    \label{tab:nc_series}
    \centering
    \begin{tabular}{cccccccc}
        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
        \hline
        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.574 & 0.40 \\
        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.147 & 0.80 \\
        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
        \hline
    \end{tabular}
\end{table*}
\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}
